Tabular Constraint Learning

### 2016-04-11 Paper/ECAI/tabular.tex

@@

\paragraph{Constraint ordering} $\constrainttorder(\constraints,\dependencies)$ uses the DAG \dependencies in Figure \ref{fig:learning_order} in the following way: all constraints are generated in the topological order of \dependencies. Also, if there is a construction edge from $C_1$ to $C_2$, and $X$ is not a solution to $C_1$, then $X$ is not generated as a candidate group for $C_2$. If there is a reversed specificity edge from $C_1$ to $C_2$ and $X$ is a solution to $C_1$, then $X$ is not generated as a candidate group for $C_2$.

@@

>>>>

\samuel{2nd problem statement (from approach), remove EQUAL}

@@

\samuel{Running example (RANK?)}
\paragraph{Constraint ordering} $\constrainttorder(\constraints,\dependencies)$ uses the DAG \dependencies in Figure \ref{fig:learning_order} in the following way: all constraints are generated in the topological order of \dependencies. Also, if there is a construction edge from $C_1$ to $C_2$, and $X$ is not a solution to $C_1$, then $X$ is not generated as a candidate group for $C_2$. If there is a sumsumption edge from $C_1$ to $C_2$ and $X$ is a solution to $C_1$, then $X$ is not generated as a candidate group for $C_2$.

@@

\samuel{Move next to subgroup satisfaction search}
\section{Declarative modeling}
\sergey{We need to fit ASP, Minizinc and all that here, I mean it is supposed to be an important point after all}
